Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-12 journal paper/content/sec-intro.tex
Added a sentence, reworded some comments.

@@

\ascomment{Guy: Previously you also cited \cite{varian2018artificial,lambrecht2015can} for the same thing as \citet{bajari2018impact}. Why not now? Also, previously you explicitly mentioned "barriers to entry" and "market tipping" and "anti-trust implications". Why not now? I don't really know any of this literature, so I defer to your judgement on this ...}

\gacomment{I added back the \cite{lambrecht2015can} reference, but \cite{varian2018artificial} is a more informal discussion of these issues and not essential to include. However, even the \cite{lambrecht2015can} is relatively informal discussion of the same issues. Part of the problem that makes this tricky is that the literature on network effects is a well-developed and mature literature, but the question of whether data plays a similar role primarily started as more of a policy discussion, of which there's only starting to be some serious theoretical and empirical work on the issue.}

\ascomment{We could, in principle, move both "Econ interpretation" xhdrs to a separate subsection. But the current order of presentation seems better to me: we can explain the inverted-U right after "theory", before we put a whole bunch of simulation results on the stack. And the anti-trust stuff goes nicely right after the numerical results, without a big subsection break.}

>>>>

\asedit{While this material builds on a vast and active research area, we present sufficient background in Section~\ref{sec:related-classes}, so as to keep this paper accessible to non-specialists.}

@@

\ascomment{Guy: citing \citet{varian2018artificial} might serve us, even if it is a more informal discussion. The existence of the policy discussion is worth mentioning, too (with citations).}

\ascomment{"Econ interpretation" xhdrs fit incely in "our results", as opposed to a separate subsection. Because: we can explain the "inverted-U" stuff right after "theory", before we put the simulation results on the stack. And the "network effects" stuff goes nicely right after the numerical results, without a big subsection break.}
